#Reproducible Research - Peer Assessment 1
<br>

##Loading and preprocessing the data
###Load libraries
```{r}
library(plyr)
```
###Load the data for this project from the working directory
```{r}
activityData <- read.csv('activity.csv')
```
<br>

##What is mean total number of steps taken per day?
###Calculate the number of steps taken per day
```{r}
stepsPerDay <- tapply(activityData$steps, activityData$date, sum, na.rm=TRUE)
```
###Histogram of the total number of steps taken each day
```{r}
hist(x=stepsPerDay,col="red",breaks=30,xlab="Daily total steps",ylab="Frequency",main="Histogram of Steps Taken per Day")
```

###Calculate and report the mean and median of the total number of steps taken per day
```{r}
meanSteps <- mean(stepsPerDay)
medianSteps <- median(stepsPerDay)
```
Mean = `r meanSteps`  
Median = `r medianSteps`
<br>
<br>

## What is the average daily activity pattern?
###Calculate the average of steps taken per interval
```{r}
stepsPerInterval <- ddply(activityData,c("interval"),summarize,meanSteps=mean(steps, na.rm=TRUE))
```
###Plot average number of steps per interval
```{r}
plot(stepsPerInterval$interval,stepsPerInterval$meanSteps,type="l",xlab="Interval",ylab="Average Steps Per Interval",main="Average Steps across all days")
```

###Detemine interval with maximum average number of steps
```{r}
maxSteps <- max(stepsPerInterval$meanSteps)
maxSteps
maxStepsInterval <- subset(stepsPerInterval, meanSteps==maxSteps)
maxStepsInterval$interval
```

Maximum Steps = `r maxSteps`  
Interval with maximum steps = `r maxStepsInterval$interval`  
<br>

##Imputing missing values
###Calculate and Report number of rows with missing steps
```{r}
countNA <- sum(is.na(activityData$steps))
```
Number of rows with missing steps = `r countNA`
<br>

###Fill in NAs with interval average
```{r}
imputedData <- merge(activityData,stepsPerInterval,by.x="interval",all=TRUE)
nas <- is.na(imputedData$steps)
imputedData$steps[nas] <- imputedData$meanSteps[nas]
stepsPerDayImputed <- tapply(imputedData$steps, imputedData$date, sum, na.rm=TRUE)
```

###Histogram of the total number of steps taken each day - NAs replaced with interval average
```{r}
hist(x=stepsPerDayImputed,col="green",breaks=30,xlab="Daily total steps",ylab="Frequency",main="Histogram of Steps Taken per Day")
```

###Calculate and report the mean and median of the total number of steps taken per day - NAs replaced with interval average
```{r}
meanStepsImputed <- mean(stepsPerDayImputed)
meanStepsImputed
medianStepsImputed <- median(stepsPerDayImputed)
medianStepsImputed
```
Mean = `r meanStepsImputed`  
Median = `r medianStepsImputed`


<br>

## Are there differences in activity patterns between weekdays and weekends?


