## Loading and preprocessing the data
## What is mean total number of steps taken per day?
## What is the average daily activity pattern?
## Imputing missing values
## Are there differences in activity patterns between weekdays and weekends?

#Reproducible Research - Peer Assessment 1
## Load libraries and data
###Load libraries
```{r}
library(ggplot2)
```

###Load the data for this project from the working directory

```{r}
activityData <- read.csv('activity.csv')
```



##What is mean total number of steps taken per day?

###Calculate the number of steps taken per day

```{r}
stepsPerDay <- tapply(activityData$steps, activityData$date, sum, na.rm=TRUE)
```

###Make a histogram of the total number of steps taken each day

```{r}
qplot(stepsPerDay, xlab="Total steps per day", ylab="Frequency", binwidth=500)
```

###Calculate and report the mean and median of the total number of steps taken per day

```{r}
meanSteps <- mean(stepsPerDay)
medianSteps <- median(stepsPerDay)
```

Mean = `r meanSteps`  
Median = `r medianSteps`

